---
title: "Lab-14 Replication"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introductions
This is the replication file for the lab for lecture-15.

## Dependencies
This lab requires the following packages:

```{r}
library(car)      # model testing
library(dplyr)    # data cleaning
library(ggplot2)  # data plotting
library(moments)  # skew and kurtosis
library(nortest)  # shapiro-francia test
```


## Data Preparation and Plotting
The data needed for the lab comes from the `testDriveR` package:

```{r}
library(testDriveR)
autoData <- auto17
```

## Part 1
### Questions 1 and 2
The following code selects the requested variables from **Question 1** and then converts the `driveStr2` variable to a favor as requested in **Question 2**.

```{r}
autoData %>%
  select(id, hwyFE, driveStr2) %>%
  mutate(driveFac = as.factor(driveStr2)) -> autoData
```

### Question 3
The following code creates a box plot of the differences in highway fuel efficiency by drive-train:

```{r}
ggplot(data = autoData, mapping = aes(x = driveFac, y = hwyFE, fill = driveFac)) + 
  geom_boxplot() +
  labs(
    title = "Highway Fuel Efficiency by Drivetrain Type",
    subtitle = "Select American Automobiles",
    x = "Drivetrain",
    y = "Highway Fuel Efficiency (mpg)",
    caption = "Data via ggplot2\nPlot produced by Christopher Prener, Ph.D."
  ) +
  theme(legend.position="none")
```

We can see from the plot that 2-wheel drive, front vehicles have the most efficiency on the highway while other forms of drive-trains have considerably worse fuel efficiency (with some outliers, for example, in the 2-wheel drive, rear category).

### Question 4
The following code groups the output by drive-train type and then calculates mean highway fuel efficiency with the grouped data:

```{r}
autoData %>%
  group_by(driveFac) %>%
  summarise(count = n(), meanHwy = mean(hwyFE))
```

The table clarifies the above plot, and also makes it clear that the low numbers for the final category, part-time 4-wheel drive, may be driven by few vehicles in the category.

## Part 2 - Assess Assumptions
### Question 5
The Bartlett Test is used to check the homogeneity of variance assumption within categorical variables.

```{r}
bartlett.test(hwyFE ~ driveFac, data = autoData)
```

The results of the Bartlett Test (${K}^{2} = 67.591, p < .001$) suggest that the homogeneity of variance assumption does not hold for these data.

### Question 6
We can evaluate normality using skew, kurtosis, a Q-Q plot, and the Shapiro-Francia test:

```{r}
skewness(autoData$hwyFE)
kurtosis(autoData$hwyFE)
```

Both the skewness and kurtosis values are well within the acceptable limits for a distribution to be considered normal.

```{r}
qqnorm(autoData$hwyFE); qqline(autoData$hwyFE)
```

There are some deviations from normal in the q-q plot, but only in one tail.

```{r}
sf.test(autoData$hwyFE)
```

Unsurprisingly, given the q-q plot, the Shapiro-Francia test ($W = .977, p < .001$) is statistically significant. This suggests that the distribution may not be normally distributed.

On the whole, the data suggest that there may be some minor deviations from normal in the distribution but that these are not large. Overall, the variable appears normally distributed.

## Part 3 - Fit the ANOVA
### Question 7
The following code fits the ANOVA model and stores in an object named `model`. The findings are then summarized.

```{r}
model <- aov(hwyFE ~ driveFac, data = autoData)
summary(model)
```

The model's results suggest that there is substantial variation in highway fuel efficiency by drive-train type ($f = 180.4; p < .001$). 

### Question 8
We can use the Tukey HSD test to identify the combinations of drive-train comparisons for which there is a statistically significant difference in average highway fuel efficiency:

```{r}
TukeyHSD(model)
```

Every possible combination of comparisons is statistically significant, suggesting that there are substantial differences in the fuel efficiency between different types of automobile drive-trains.

## Part 4 - Check for Outliers
### Question 9
Finally, we should check for outliers as it is another key assumption of ANOVA:

```{r}
outlierTest(model)
```

The results of the Bonferonni test suggest that there may be a number of outliers (at least 3) that are worthy of further exploration and possible exclusion from a re-fit ANOVA model.
